### 2021-01-15 paper/localpsf.tex
more edits

Let $\delta_x$ denote the point source (delta distribution) centered at $x$. The function $\phi_x$ is called the impulse response because straightforward analysis shows that it may be expressed as follows:
\begin{equation}
\label{eq:impulse_response_delta_action}
	\phi_x = \left\langle \mathcal{A}, \delta_x \right\rangle^*,
\end{equation}
where $\left\langle \mathcal{A}, \delta_x \right\rangle \in L^2(\Omega)'$ denotes the result of applying the operator $\mathcal{A}$ to the distribution $\delta_x$, and $\left\langle \mathcal{A}, \delta_x \right\rangle^* \in L^2(\Omega)$ denotes the Riesz representation of $\langle\mathcal{A}, \delta_x\rangle$ with respect to the $L^2$ inner product.\footnote{Recall that the Riesz representative of a functional $\psi \in L^2(\Omega)'$ with respect to the $L^2$ inner product is the unique function $\psi^* \in L^2(\Omega)$ such that $\psi(v) = \left(\psi^*,v\right)_{L^2(\Omega)}$ for all $v \in L^2(\Omega)$.} The local support property says, therefore, that a point source at $x$ has zero impact (or minimal impact) on points $y$ that are far away from $x$.

Note that while the domain of $\mathcal{A}$ is defined as $L^2(\Omega)$, which does not contain the delta distribution, the application of $\mathcal{A}$ is extended to distributions in a natural way, as described in Appendix \ref{app:distributions}. 
%We take the Riesz representative of the linear functional $\left\langle \mathcal{A}, \delta_x \right\rangle \in L^2(\Omega)'$ to convert it into a function $\left\langle \mathcal{A}, \delta_x \right\rangle^* \in L^2(\Omega)$. 
After discretization, the process of applying $\mathcal{A}$ to a delta distribution, then forming the Riesz representative, amounts to computing $\boldsymbol{\phi}_x = \mathbf{M}^{-1}\mathbf{A} \mathbf{M}^{-1} \boldsymbol{\delta}_{x_i}$, where $\boldsymbol{\phi}_x$, $\mathbf{A}$, and $\boldsymbol{\delta}_x$ are discretized versions of $\phi_x$, $A$, and $\delta_x$, respectively, and $\mathbf{M}$ is a mass matrix (e.g., in a finite element context).

Local translation invariance is illustrated in Figure FIG. If $\mathcal{A}$ were perfectly translation invariant (i.e., if equality held in \eqref{eq:local_translation_invariance} for all $x$, $y$, $h$) then it is straightforward to show that $\mathcal{A}$ would be a convolution operator, and the convolution kernel, $\varphi_x$, would be given by
\begin{equation}
\label{eq:convolution_kernel}
	\varphi_x(y) := \phi_x(y+x).
\end{equation}
The convolution kernel $\varphi_x$ is the result of translating the impulse response $\phi_x$ to re-center it at zero instead of $x$. Locally translation invariant operators act like convolution operators locally, but the convolution kernel, $\varphi_x$, varies as $x$ changes. We therefore approximate $\mathcal{A}$ by a spatially varying weighted sum of convolution operators, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, of the form
\begin{equation}
\label{eq:product_convolution}
	\left(\widetilde{\mathcal{A}}u\right)(v) := \left( v,~ \sum_{i=1}^r \varphi_i \ast \left(w_i \cdot u\right) \right)_{L^2(\Omega)},
\end{equation}
where $f \cdot g$ denotes pointwise multiplication, $f \ast g$ denotes convolution, and $\left(f, g\right)_{L^2(\Omega)}$ denotes the $L^2$ inner product on $\Omega$, for functions $f,g \in L^2(\Omega)$. Here we write $\varphi_i := \varphi_{x_i}$ (with $\varphi_{x_i}$ defined in \eqref{eq:convolution_kernel}) to denote local convolution kernels corresponding to a collection of points $\{x_i\}_{i=1}^r \subset \Omega$ scattered throughout the domain. The functions $w_i$ are spatially varying weighting functions that are used to interpolate the convolution kernels $\varphi_i$. Our operator approximation method is defined by how we compute the convolution kernels, $\varphi_i$, how we choose the points, $x_i$, what weighting functions, $w_i$, that we use, and how we use the resulting product-convolution approximation to perform linear algebra operations such as solving linear systems. In Section \ref{sec:overview_intro} we summarize the answers to these questions; we will provide detailed answers to these questions in Section \ref{sec:method}.

@@

We compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a Dirac comb, then post-processing the result. That is, we compute
\begin{equation}
\label{eq:eta_intro}
\eta := \left\langle \mathcal{A}, \xi \right\rangle^*
\end{equation}
where 
\begin{equation*}
	\xi := \sum_{i=1}^l \delta_{x_i}
\end{equation*}
is the Dirac comb associated with point sources centered at a collection of scattered points $x_i$. The batch of points $x_i$ are chosen so that the support of $\phi_{x_i}$ and the support of $\phi_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$.

By linearity, and the expression for $\phi_x$ in \eqref{eq:impulse_response_delta_action}, we have
\begin{equation*}
\eta = \sum_{i=1}^l \phi_{x_i}.
\end{equation*}
Since the support of $\phi_{x_i}$ and the support of $\phi_{x_j}$ do not overlap, we may post-process $\eta$ to recover $\phi_i$, and therefore $\varphi_i$, for all of the points $x_i$ in the batch---by applying $\mathcal{A}$ to one distribution, we recover many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until a desired number of batches is reached.

In order to choose the points $x_i$, we need to estimate the support of $\phi_{x_i}$ \emph{before} we compute it. The supports of the functions $\phi_x$ are estimated a-priori, for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\mathcal{A}^T$ to a small number of specially chosen functions (three functions if $d=1$, six if $d=2$, ten if $d=3$), then post processing the results (Section \ref{eq:mean_and_covariance_estimation}). This procedure is the only part of the paper that requires non-negativity of the integral kernel.

@@

\section{Constructing the approximation}
\label{sec:method}
This section describes how we compute the convolution kernels, $\varphi_i$, and weighting functions, $w_i$, for the product-convolution approximation, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, given in \eqref{eq:product_convolution}. We also describe how we evaluate kernel entries of the approximation, $\widetilde{A}(y,x)$, and how we convert $\widetilde{\mathcal{A}}$ to H-matrix format.
\begin{itemize}
\item We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). To reduce memory usage, all kernels $\varphi_i$ associated with a given batch, $b$, are stored in a single function, $\eta^b$, rather than as distinct functions.
\item We use a greedy algorithm to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}). 
\item We ensure that the points $x_i$ are well separated from each other by forming a-priori estimates of the supports of the functions $\langle\mathcal{A},\delta_{x}\rangle^*$ (Section \ref{eq:mean_and_covariance_estimation}). 
\item For the weighting functions, we use the smoothest functions (in a least-squares sense) that interpolate the points $x_i$; constructing the weighting functions requires solving two Poisson PDEs per point $x_i$ (Section \ref{sec:weighting_functions}).
\end{itemize}
The complete algorithm for constructing $\widetilde{\mathcal{A}}$ is shown in Algorithm \ref{alg:construct_Atilde}. The method for evaluating kernel entries of $\widetilde{A}$ is shown in Section \ref{sec:eval_matrix_entries}. The method for converting $\widetilde{\mathcal{A}}$ to H-matrix format is shown in Section \ref{sec:H_matrix_conversion}. In the rest of the section we will need the following definitions.

@@

The \emph{Dirac comb}, $\xi_b$, associated with a batch of sample points $S_b$ is the sum of Dirac distributions (point sources) centered at the points $x_i \in S_b$. That is,
\begin{equation*}
	\xi^b := \sum_{x_i \in S_b} \delta_{x_i}.
\end{equation*}
For each batch $S_b$, we compute as the action of $\mathcal{A}$ on the associated Dirac comb:
\begin{equation}
\label{eq:dirac_comb_H_action}
	\eta^b := \langle\mathcal{A}, \xi^b\rangle^*.
\end{equation}
By linearity, $\eta^b$ may be written as
\begin{equation}
\label{eq:phi_b}
	\eta^b = \left\langle\mathcal{A},\sum_{x_i \in S_b} \delta_{x_i}\right\rangle^* = \sum_{x_i \in S_b} \langle\mathcal{A}, \delta_{x_i}\rangle^*.
\end{equation}
Since the points $x_i$ are chosen so that the support of $\langle\mathcal{A},\delta_{x_i}\rangle^*$ and the support of $\langle\mathcal{A},\delta_{x_j}\rangle^*$ do not overlap (or do not overlap much), we have
\begin{equation}
\label{eq:varphi_eval}
	\varphi_{x_i}(z) = \langle\mathcal{A}, \delta_{x_i}\rangle^*(z+x_i) = \begin{cases}
		\eta^b(z+x_i), & z+x_i \in E_{x_i} \\
		0, & \text{otherwise}.
		\end{cases}
\end{equation}
for all $x_i \in S_b$. By performing one matrix-vector product, \eqref{eq:dirac_comb_H_action}, we recover $\varphi_{x_i}$ for every point $x_i \in S_b$. To minimize memory usage, the functions $\varphi_i$ are never isolated and stored individually. Instead, we store the functions $\eta^b$, and use formula \eqref{eq:varphi_eval} to perform function evaluations $z \mapsto \varphi_i(z)$ as needed.

@@

\begin{thm}[Optimal interpolation]
	\label{thm:smoothest_interpolant}
Let $y \in \mathbb{R}^d$, and let $u$ be the function
\begin{equation}
\label{eq:u_defn_in_thm}
u(x) := \sum_{i=1}^r \varphi_i(y)w_i(x) = \widetilde{A}\left(y+x,x\right)
\end{equation}
where the weighting functions $w_i$ are the solutions to optimization problem \eqref{eq:wi_optimization_problem}. Then $u$ solves the optimization problem
\begin{equation}
\label{eq:uy_optimization_problem}
\begin{aligned}
\min_{u \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta u}_{L^2(\Omega)}^2 \\
\text{such that} &\quad u(x_i) = \varphi_i(y), \quad i=1,\dots,q.
\end{aligned}
\end{equation}
\end{thm}

@@

\begin{lem}[Preparation for Theorem \ref{thm:smoothest_interpolant}]
	\label{lem:T_is_linear}
	Let $f \in \mathbb{R}^r$. There exists a unique solution to the following optimization problem:
	\begin{equation}
	\label{eq:generic_optimization_initial}
	\begin{aligned}
	\min_{u \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta u}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad u(x_i) = f_i, \quad i=1,\dots,r.
	\end{aligned}
	\end{equation}
	Let $\mathcal{T}:\mathbb{R}^r \rightarrow H^2(\Omega)$ denote the solution operator for optimization problem \eqref{eq:generic_optimization_initial}	as a function of $f$. That is, 
	\begin{equation*}
	\mathcal{T}(f) := u^*,
	\end{equation*}
	where $u^*$ is the minimizer of \eqref{eq:generic_optimization_initial}. The operator $\mathcal{T}$ is a linear operator.
\end{lem}
\begin{proof}
	WRITE THIS PROOF
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:smoothest_interpolant}]
	Let $f = (\varphi_1(y), \varphi_2(y), \dots, \varphi_r(y))$ and let $e_i = (0,\dots,0,1,0,\dots,0)$ be the length $r$ vector with $i^\text{th}$ component equal to one and all other components equal to zero. The solution to optimization problem \eqref{eq:uy_optimization_problem} is given by
	\begin{align*}
	\mathcal{T}(f) &= \varphi_1(y) \mathcal{T}(e_1) + \varphi_2(y) \mathcal{T}(e_2) + \dots +\varphi_r(y) \mathcal{T}(e_r) \\
	&= \varphi_1(y) w_1 + \varphi_2(y) w_2 + \dots +\varphi_r(y) w_r \\
	&= u.
	\end{align*}
	In the first line we used linearity of the solution map, $\mathcal{T}$ (Lemma \ref{lem:T_is_linear}), in the second line we used the fact that $w_i = \mathcal{T}(e_i)$, and in the third line we used the definition of $u$ in \eqref{eq:u_defn_in_thm}.
\end{proof}

>>>>

Let $\delta_x$ denote the point source (delta distribution) centered at $x$. The function $\phi_x$ is called the impulse response because straightforward analysis shows that it may be expressed as follows:
\begin{equation}
\label{eq:impulse_response_delta_action}
	\phi_x = \left\langle \mathcal{A}, \delta_x \right\rangle^*,
\end{equation}
where $\left\langle \mathcal{A}, \delta_x \right\rangle \in L^2(\Omega)'$ denotes the result of applying the operator $\mathcal{A}$ to the distribution $\delta_x$, and $\left\langle \mathcal{A}, \delta_x \right\rangle^* \in L^2(\Omega)$ denotes the Riesz representation of $\langle\mathcal{A}, \delta_x\rangle$ with respect to the $L^2$ inner product.\footnote{Recall that the Riesz representative of a functional $\psi \in L^2(\Omega)'$ with respect to the $L^2$ inner product is the unique function $\psi^* \in L^2(\Omega)$ such that $\psi(v) = \left(\psi^*,v\right)_{L^2(\Omega)}$ for all $v \in L^2(\Omega)$.} Note that while the domain of $\mathcal{A}$ is defined as $L^2(\Omega)$, which does not contain $\delta_x$, the action of $\mathcal{A}$ may be extended to distributions in a natural way, as described in Appendix \ref{app:distributions}. 
%The action of $\mathcal{A}$ on a distribution $\mu$ is written as $\langle \mathcal{A}, \mu \rangle$. We use this angle bracket notation to distinguish the action of $\mathcal{A}$ on distributions from the action of $\mathcal{A}$ on functions.
%We take the Riesz representative of the linear functional $\left\langle \mathcal{A}, \delta_x \right\rangle \in L^2(\Omega)'$ to convert it into a function $\left\langle \mathcal{A}, \delta_x \right\rangle^* \in L^2(\Omega)$. 
After discretization, the process of applying $\mathcal{A}$ to the distribution $\delta_x$, then forming the Riesz representative of the resulting linear functional, amounts to computing $\boldsymbol{\phi}_x = \mathbf{M}^{-1}\mathbf{A} \mathbf{M}^{-1} \boldsymbol{\delta}_x$, where $\boldsymbol{\phi}_x$, $\mathbf{A}$, and $\boldsymbol{\delta}_x$ are discretized versions of $\phi_x$, $A$ and $\delta_x$, respectively, and $\mathbf{M}$ is a discretization of the $L^2$ inner product bilinear form (e.g., a mass matrix in the finite element context). From \eqref{eq:impulse_response_delta_action}, we see that the local support property means that the response of $\mathcal{A}$ to a point source at $x$ is zero (or small) at points $y$ that are far from $x$.

Local translation invariance is illustrated in Figure FIG. If $\mathcal{A}$ were perfectly translation invariant (i.e., if equality held in \eqref{eq:local_translation_invariance} for all $x$, $y$, $h$) then it is straightforward to show that $\mathcal{A}$ would be a convolution operator, and the convolution kernel, $\varphi_x$, would be given by
\begin{equation}
\label{eq:convolution_kernel}
	\varphi_x(y) := \phi_x(y+x).
\end{equation}
The convolution kernel $\varphi_x$ is the result of translating the impulse response $\phi_x$ to re-center it at zero instead of $x$. Locally translation invariant operators act like convolution operators locally, but the convolution kernel, $\varphi_x$, varies as $x$ changes. We therefore approximate $\mathcal{A}$ by a spatially varying weighted sum of convolution operators, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, of the form
\begin{equation}
\label{eq:product_convolution}
	\left(\widetilde{\mathcal{A}}u\right)(v) := \left( v,~ \sum_{i=1}^r \varphi_i \ast \left(w_i \cdot u\right) \right)_{L^2(\Omega)},
\end{equation}
where $f \cdot g$ denotes pointwise multiplication, $f \ast g$ denotes convolution, and $\left(f, g\right)_{L^2(\Omega)}$ denotes the $L^2$ inner product on $\Omega$, for functions $f,g \in L^2(\Omega)$. To avoid nested subscripts, we write 
\begin{equation*}
\varphi_i := \varphi_{x_i} \quad \text{and} \quad \phi_i := \phi_{x_i},
\end{equation*}
with $\varphi_{x_i}$ defined in \eqref{eq:convolution_kernel} and $\phi_{x_i}$ defined in \eqref{eq:impulse_response_defn}, to denote local convolution kernels and impulse responses corresponding to a collection of points $\{x_i\}_{i=1}^r \subset \Omega$ scattered throughout the domain.  The functions $w_i$ are spatially varying weighting functions that are used to interpolate the convolution kernels $\varphi_i$. Our operator approximation method is defined by how we compute the convolution kernels, $\varphi_i$, how we choose the points, $x_i$, what weighting functions, $w_i$, that we use, and how we use the resulting product-convolution approximation to perform linear algebra operations such as solving linear systems. In Section \ref{sec:overview_intro} we summarize the answers to these questions; we will provide detailed answers to these questions in Section \ref{sec:method}.

@@

We compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a sum of point sources (Dirac comb) associated with a collection of points $x_i$ scattered throughout $\Omega$. The batch of points $x_i$ are chosen so that the support of $\phi_i$ and the support of $\phi_j$ do not overlap (or do not overlap much) if $i \neq j$. Because these supports do not overlap, we can post-process the response of $\mathcal{A}$ to the Dirac comb to recover the functions $\phi_i$, and therefore the functions $\varphi_i$, associated with all points $x_i$ in the batch---with one application of $\mathcal{A}$, we recover many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until a desired number of batches is reached.

%First, we compute
%\begin{equation}
%\label{eq:eta_intro}
%\eta := \left\langle \mathcal{A}, \xi \right\rangle^*
%\end{equation}
%where 
%\begin{equation*}
%	\xi := \sum_{i=1}^l \delta_{x_i}
%\end{equation*}
%is the Dirac comb associated with point sources centered at a collection of scattered points $x_i$. The batch of points $x_i$ are chosen so that the support of $\phi_i$ and the support of $\phi_j$ do not overlap (or do not overlap much) if $i \neq j$. By linearity, and the expression for $\phi_x$ in \eqref{eq:impulse_response_delta_action}, we have
%\begin{equation*}
%\eta = \sum_{i=1}^l \phi_i.
%\end{equation*}
%We may therefore post-process $\eta$ 
%
%to recover $\phi_i$ for all of the points $x_i$ in the batch. Since the functions $\varphi_i$ are translated versions of the functions $\phi_i$, we also recover $\varphi_i$ for all points $x_i$ in the batch. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until a desired number of batches is reached.

In order to choose the points $x_i$, we need to estimate the support of $\phi_i$ \emph{before} we compute it. The supports of the functions $\phi_x$ are estimated a-priori, for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\mathcal{A}^T$ to a small number of specially chosen functions (three functions if $d=1$, six if $d=2$, ten if $d=3$), then post processing the results (Section \ref{eq:mean_and_covariance_estimation}). This procedure is the only part of the paper that requires non-negativity of the integral kernel.

@@

\section{Constructing the approximation}
\label{sec:method}
This section describes how we compute the convolution kernels, $\varphi_i$, and weighting functions, $w_i$, for the product-convolution approximation, $\widetilde{\mathcal{A}} \approx \mathcal{A}$, given in \eqref{eq:product_convolution}. We also describe how we evaluate kernel entries of the approximation, $\widetilde{A}(y,x)$, and how we convert $\widetilde{\mathcal{A}}$ to H-matrix format.
\begin{itemize}
\item We extract $\varphi_{x_i}$ for many points $x_i$ by applying $\mathcal{A}$ to Dirac combs associated with ``batches'' of points (Section \ref{sec:get_impulse_response}). To reduce memory usage, all kernels $\varphi_i$ associated with a given batch, $b$, are stored in a single function, $\eta^b$, rather than as distinct functions.
\item We use a greedy algorithm to choose as many points as possible per batch, while ensuring that the points in each batch are not too close to each other, and are not too close to $\partial \Omega$ (Section \ref{sec:greedy_point_selection}). 
\item We ensure that the points $x_i$ are well separated from each other by forming a-priori estimates of the supports of the functions $\psi_x$ (Section \ref{eq:mean_and_covariance_estimation}). 
\item For the weighting functions, we use the smoothest functions (in a least-squares sense) that interpolate the points $x_i$; constructing the weighting functions requires solving two Poisson PDEs per point $x_i$ (Section \ref{sec:weighting_functions}).
\end{itemize}
The complete algorithm for constructing $\widetilde{\mathcal{A}}$ is shown in Algorithm \ref{alg:construct_Atilde}. The method for evaluating kernel entries of $\widetilde{A}$ is shown in Section \ref{sec:eval_matrix_entries}. The method for converting $\widetilde{\mathcal{A}}$ to H-matrix format is shown in Section \ref{sec:H_matrix_conversion}. In the rest of the section we will need the following definitions.

@@

The \emph{Dirac comb}, $\xi_b$, associated with a batch of sample points $S_b$ is the sum of Dirac distributions (point sources) centered at the points $x_i \in S_b$. That is,
\begin{equation*}
	\xi^b := \sum_{x_i \in S_b} \delta_{x_i}.
\end{equation*}
For each batch $S_b$, we compute as the action of $\mathcal{A}$ on the associated Dirac comb:
\begin{equation}
\label{eq:dirac_comb_H_action}
	\eta^b := \langle\mathcal{A}, \xi^b\rangle^*.
\end{equation}
By linearity, $\eta^b$ may be written as
\begin{equation}
\label{eq:phi_b}
	\eta^b = \left\langle\mathcal{A},\sum_{x_i \in S_b} \delta_{x_i}\right\rangle^* = \sum_{x_i \in S_b} \langle\mathcal{A}, \delta_{x_i}\rangle^* = \sum_{x_i \in S_b} \phi_x.
\end{equation}
Since the points $x_i$ are chosen so that the support of $\phi_i$ and the support of $\phi_j$ do not overlap (or do not overlap much), we have
\begin{equation}
\label{eq:varphi_eval}
	\varphi_{x_i}(z) = \phi_i(z+x_i) = \begin{cases}
		\eta^b(z+x_i), & z+x_i \in E_{x_i} \\
		0, & \text{otherwise}.
		\end{cases}
\end{equation}
for all $x_i \in S_b$. By performing one matrix-vector product, \eqref{eq:dirac_comb_H_action}, we recover $\varphi_{x_i}$ for every point $x_i \in S_b$. To minimize memory usage, the functions $\varphi_i$ are never isolated and stored individually. Instead, we store the functions $\eta^b$, and use formula \eqref{eq:varphi_eval} to perform function evaluations $z \mapsto \varphi_i(z)$ as needed.

@@

\begin{thm}[Optimal interpolation]
	\label{thm:smoothest_interpolant}
Let $y \in \mathbb{R}^d$, and let $\gamma_y$ be the function
\begin{equation}
\label{eq:u_defn_in_thm}
\gamma_y(x) := \sum_{i=1}^r \varphi_i(y)w_i(x) = \widetilde{A}\left(y+x,x\right)
\end{equation}
where the weighting functions $w_i$ are the solutions to optimization problem \eqref{eq:wi_optimization_problem}. Then $\gamma_y$ solves the optimization problem
\begin{equation}
\label{eq:uy_optimization_problem}
\begin{aligned}
\min_{\gamma_y \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta \gamma_y}_{L^2(\Omega)}^2 \\
\text{such that} &\quad \gamma_y(x_i) = \varphi_i(y), \quad i=1,\dots,q.
\end{aligned}
\end{equation}
\end{thm}

@@

\begin{lem}[Preparation for Theorem \ref{thm:smoothest_interpolant}]
	\label{lem:T_is_linear}
	Let $f \in \mathbb{R}^r$. There exists a unique solution to the following optimization problem:
	\begin{equation}
	\label{eq:generic_optimization_initial}
	\begin{aligned}
	\min_{\gamma \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta \gamma}_{L^2(\Omega)}^2 \\
	\text{such that} &\quad \gamma(x_i) = f_i, \quad i=1,\dots,r.
	\end{aligned}
	\end{equation}
	Let $\mathcal{T}:\mathbb{R}^r \rightarrow H^2(\Omega)$ denote the solution operator for optimization problem \eqref{eq:generic_optimization_initial}	as a function of $f$. That is, 
	\begin{equation*}
	\mathcal{T}(f) := \gamma^*,
	\end{equation*}
	where $\gamma^*$ is the minimizer of \eqref{eq:generic_optimization_initial}. The operator $\mathcal{T}$ is a linear operator.
\end{lem}
\begin{proof}
	WRITE THIS PROOF
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:smoothest_interpolant}]
	Let $f = (\varphi_1(y), \varphi_2(y), \dots, \varphi_r(y))$ and let $e_i = (0,\dots,0,1,0,\dots,0)$ be the length $r$ vector with $i^\text{th}$ component equal to one and all other components equal to zero. The solution to optimization problem \eqref{eq:uy_optimization_problem} is given by
	\begin{align*}
	\mathcal{T}(f) &= \varphi_1(y) \mathcal{T}(e_1) + \varphi_2(y) \mathcal{T}(e_2) + \dots +\varphi_r(y) \mathcal{T}(e_r) \\
	&= \varphi_1(y) w_1 + \varphi_2(y) w_2 + \dots +\varphi_r(y) w_r \\
	&= \gamma_y.
	\end{align*}
	In the first line we used linearity of the solution map, $\mathcal{T}$ (Lemma \ref{lem:T_is_linear}), in the second line we used the fact that $w_i = \mathcal{T}(e_i)$, and in the third line we used the definition of $\gamma_y$ in \eqref{eq:u_defn_in_thm}.
\end{proof}
